---
title: "Apple shares dumb forecasting investment strategy (or how to invest, and then again, maybe not... )"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
---

```{r setup, include=FALSE}
source("../include.R")
if (!require("flexdashboard")) {
  install.packages("flexdashboard", type = "source")
  library(flexdashboard)
}
d <- getSymbolPrices("AAPL", c("1980-01-01","2018-12-01"))
d$forecast <- getWindowForecasts(d$close, 28, 7)
d$position <- getPositions(d, "close", "forecast", 29, 7)
d$balance <- getBalance(d, "close", "position")
```

### shares historical daily data overview

```{r}

    chartSeries(d, theme = "white", name = "Apple")

```

***

here we can have an overview of historical data:

- daily close prices

- daily trading volumes



### shares historical daily data drill down

```{r}

    ts_plot(d[,c("close", "volume")], Xgrid = TRUE, Ygrid = TRUE, slider = TRUE)

```

***

here we can inspect and drill down into historical data:

- daily close prices

- daily trading volumes

We can zoom into the historical data.


### shares daily close price and forecast

```{r}

     ts_plot(d[,c("close", "forecast")], type = "single", Xgrid = TRUE, Ygrid = TRUE, Ytitle = "share price",slider = TRUE, line.mode = "lines+markers")

```

***

here we can see a close price forecast:

- arima model automatically determined;

- training window = 28 days;

- forecasting window = 7 days;

There is an initial training period and a forecast of a set of points, in this case 7 days, the forecasting window. 
After that the training period aligns in order to forecast into the following forecasting windows after those initial 7 days.

### dumb investment position simulation and related balance, based on forecast

```{r}

     ts_plot(d[,c("position", "balance")], Xgrid = TRUE, Ygrid = TRUE, line.mode = "lines+markers", slider = TRUE)

```

***

here we can analyse the outcome of a dumb investment strategy:

- at every end of training window we have a forecast for the next 7 days;

- if the close price in 7 days, provided by forecast, is above the current close price, we buy;

- if it is lower than the current close price, we sell;

- the simulation operation, buy or sell, is to be executed on a single share;





